### 2023-01-17 output/DiD/tables/balance_table.tex
Updated Zestimates in summary statistics

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{3}{3cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 & 0.01 & 0.47 \\
 & No cause & 0.11 & -0.03 & 0.03 & -0.03 & 0.05 \\
 & Non-payment of rent & 0.72 & -0.01 & 0.76 & -0.01 & 0.73 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 & -0.12 & 0.00 \\
 & Plaintiff has an attorney & 0.80 & 0.01 & 0.48 & 0.01 & 0.47 \\
 & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.00 & 0.47 \\
 & Plaintiff is an entity & 0.66 & 0.03 & 0.12 & 0.03 & 0.13 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52,087.32 & 0.04 & 0.00 & 0.03 & 0.01 \\
 & Population density (2010) & 9,031.64 & 0.06 & 0.25 & 0.06 & 0.24 \\
 & Portion white (2010) & 0.60 & 0.06 & 0.01 & 0.05 & 0.02 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{3}{3cm}{\textit{Panel A: Pre-treatment Zestimates}} & Jan. 2017 & 291,942.14 & 26,570.00 & 0.00 & 17,563.13 & 0.03 \\
 & Jan. 2018 & 320,170.03 & 27,148.19 & 0.00 & 17,292.03 & 0.05 \\
 & Change from Jan. 2018 to Jan. 2019 & 22,263.71 & 2,086.50 & 0.21 & 1,336.20 & 0.43 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Median household income (2016) & 52,087.32 & 2,566.82 & 0.01 & 1,838.37 & 0.08 \\
 & Population density (2010) & 9,031.64 & 944.99 & 0.01 & 715.29 & 0.05 \\
 & Portion white (2010) & 0.60 & 0.04 & 0.00 & 0.03 & 0.02 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 & 0.01 & 0.54 \\
 & No cause & 0.11 & -0.03 & 0.03 & -0.03 & 0.04 \\
 & Non-payment of rent & 0.72 & -0.01 & 0.76 & -0.01 & 0.67 \\
\cline{1-7}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 & -0.12 & 0.00 \\
 & Plaintiff has an attorney & 0.80 & 0.01 & 0.48 & 0.01 & 0.59 \\
 & Defendant is an entity & 0.01 & 0.00 & 0.37 & 0.00 & 0.57 \\
 & Plaintiff is an entity & 0.66 & 0.03 & 0.12 & 0.03 & 0.18 \\
\cline{1-7}
\bottomrule
\end{tabular}
